The Development of a Collaborative Tool to Teach Debugging

### 2020-11-24 paper/paper.tex
lots of little QOL things'

\begin{figure}[h!]
  \begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
    % uncomment if require: \path (0,494); %set diagram left start at 0, and has height of 494

@@

>>>>

\begin{figure}[h!]

  \begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
    % uncomment if require: \path (0,494); %set diagram left start at 0, and has height of 494

@@

Kubernetes is the defacto standard in container orchestration
software.  It provides a layer of abstraction on top of normal
containers, like those created by Docker.  By bundling one or more
closely linked containers into a ``pod'', Kubernetes is able to manage
deployment and re-deployment of applications running inside
containers.  It is trivial to create new pods, or to create multiple
pods running the same application as needed within a Kubernetes
cluster.  Kubernetes provides services to facilitate load balancing,
manage storage volumes,
